\documentclass[margin,line]{resume}

\usepackage{paralist}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Ashwin Lakshmanan}


\begin{resume}

    %__________________________________________________________________________________________________________________
    %Contact Information
    \section{\mysidestyle Contact Information}
    
    
    \textit{Mobile:} +91 8891 494 912    \hfill    \textit{e-mail:} ashwin.lakshmanan@yahoo.co.in
        
      \vspace{+0.5mm}
	
	
    %__________________________________________________________________________________________________________________
    % Objective
    \section{\mysidestyle Career Objective}

        To develop software that would help ease the lives of people by utilizing and simultaneously nurturing my skills in computer science.

										
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{National Institute of Technology Calicut} \hfill Calicut, Kerala, India
    \\
    \textit{B.Tech, Computer Science and Engineering} \hfill \textit{ July 2010 -- May 2014}
    
    \begin{compactitem}
        \item[--] \textit{Cumulative GPA:} 9.20 
        \item[--] \textit{Relevant Courses}: Data Structures \& Algorithms, Design \& Analysis of Algorithms, Operating Systems, Computer Organization, Computer Architecture, Computer Networks, Discrete Structures, Compilers, Databases, Computer Security, Natural Language Processing.
    \end{compactitem}
    
    \vspace{2mm}
    
    \textbf{Institute of Mathematical Sciences Chennai} \hfill Chennai, Tamil Nadu, India
    \\
    \textit{Summer school} \hfill \textit{ May 2012 -- June 2012}
    
    \begin{compactitem}
        \item[--] Attended lectures on graph theory, randomization and approximation 
        \item[--] Attended a Network Optimization and Security Workshop as part of the course
    \end{compactitem}
    
    \vspace{2mm}
    
    \textbf{Kendriya Vidyalaya No. 1} \hfill Palakkad, Kerala, India 
    \vspace{+0.5mm}
    \begin{compactitem}
        \item[--] Class XII (CBSE) : 95.4\%    \hfill    \textit{2010}
        \item[--] Class X (CBSE) : 92\%        \hfill    \textit{2008}
    \end{compactitem}

    %__________________________________________________________________________________________________________________
    % Projects
    \section{\mysidestyle Projects}

	
    \textbf{A Simple E-Voting Protocol} 				\hfill NIT Calicut 
    \\
    \textit{Supervisor: Dr. Vinod Pathari } 			\hfill \textit{August 2013 -- Present}
    \\
    \textit{Technologies: Java, PHP, MySQL, JavaScript}
    \\
    A simple electronic voting protocol that provides the ability to recast and also satisfies most e-voting requirements.
    
    \textbf{High Performance Computing \& Virtualization in the Cloud} 				\hfill NIT Calicut
    \\
    \textit{Supervisor: Dr. Vineeth Paleri } 			\hfill \textit{December 2012 -- May 2014}
    \\
    \textit{Technologies: Eucalyptus Cloud, Rocks Cluster, Shell Scripting, Linux Networking}
    \\
    Set up a scalable private cloud in the campus using open source tools like Eucalyptus and Rocks,
capable of high performance computing and virtualization providing IaaS for the student community in campus.
	
	\vspace{2mm}%

	\textbf{Simple Integer Language (SIL) Compiler} 						\hfill NIT Calicut
	\\
    \textit{Class Project, Compiler Design} 	\hfill \textit{January 2013 -- May 2013}
    \\
	Engineered a compiler for a simple \& strongly typed language, SIL in C using tools like LEX and YACC.
  
   \vspace{2mm}%
   
      
   %__________________________________________________________________________________________________________________
   %  Experience
    \section{\mysidestyle Experience } 
	 \textbf{Summer Internship at Amazon IDC} \hfill Bangalore, Karnataka, India
	 \\
     \textit{SDE Intern} \hfill \textit{April 2012 -- June 2013}
    
    \begin{compactitem}
        \item[--] Developed a device health monitoring daemon for kindle using android SDK
        \item[--] Implemented a workflow manager for Test                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           As A Service(TAAS) using Amazon SQS.
    \end{compactitem}
    
    \vspace{2mm}
    
    %__________________________________________________________________________________________________________________
    %  Responsibilities Held
    \section{\mysidestyle Responsibilities Held } 
	
	\begin{list2}
	\item[--] Lab Administrator (Software Systems Laboratory) \hfill \textit{August 2013 -- May 2014}
	\item[--] HPC Administrator (Biocomputing Laboratory)  \hfill  \textit{August 2012 -- May 2014}
	\item[--] Member of core team of FOSSMeet 2014.
	\end{list2}

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming Skills} 
    	\begin{list2}
	\item[-] Proficient in C, Java and Shell Scripting
	\item[-] Experience in working with python, PHP, JavaScript, HTML/CSS, MySQL
	\item[-] Comfortable with Linux and Windows environments
	\end{list2}
	
	
	
	   %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Extra Curricular Activities} 
    	\begin{list2}
	\item[-] Awarded Rajya Puraskar award for serving in The Bharat Scouts and Guides
	\item[-] Served as a Manager of Ethnic Stall, Tathva '14 (Tech fest, NIT Calicut)
	\item[-] Represented Kendriya Vidyalaya, Palakkad at the regional level under-17 chess tournament at Chennai
	\item[-] Participated in the national level science exhibition conducted at Lucknow by Kendriya
Vidyalaya Sangathan
	\end{list2}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}
